How to select predictive models for decision-making or causal inference?

### 2023-12-13 how_to_select_causal_models.tex
condense: move datasplit result in appendix

@@

\paragraph{Use 90\% of the data to estimate outcome models, 10\% to
    select them}

@@

\paragraph{Selecting different seeds and parameters is crucial to draw
    conclucions}\label{{apd:results:seed_effect}}

@@

\section{Heterogeneity in practices for data split}\label{apd:results:k_fold_choices}

>>>>

Practically, we recommand a train/test split of 90 \%/10\%. Use most of the data
to estimate both the nuisances and outcome models, then compute the risks on the
remaining test set for model selection (emprical argument in Appendix
\ref{apd:results:data_split}).

@@

@@

\paragraph{Selecting different seeds and parameters is crucial to draw
    conclusions}\label{{apd:results:seed_effect}}

@@

\section{Data split choices}\label{apd:results:data_split}

\subsection{Use 90\% of the data to estimate outcome models, 10\% to
    select them}

\subsection{Heterogeneity in practices for data split}\label{apd:results:k_fold_choices}
